% ===============================
% Professional Experience
% ===============================
\section{Professional Experience}

\cventry{June 2023 -- June 2024}{Head of DevOps & Infrastructure}{\textbf{Company A}}{City, Country}{}{
\begin{itemize}
    \item Led and restructured the IT Infrastructure, DevOps, and Support teams, expanding the team to 20 members.
    \item Managed IT operations, ensuring high-quality hardware and software support.
    \item Handled IT budget, contracts, and service agreements.
    \item Implemented ITSM and CMDB tools, improving service delivery and compliance.
    \item Ensured IT security, implementing best practices and adhering to regulatory requirements.
\end{itemize}
}

\cventry{Feb 2021 -- June 2023}{Team Leader, Systems Administrators Team}{\textbf{Company B}}{City, Country}{}{
\begin{itemize}
    \item Managed and coached a team of 5 engineers, overseeing critical IT infrastructures for research and education.
    \item Implemented continuous improvement processes and ensured operational IT.
    \item Managed new IT needs, deploying appropriate solutions based on user requirements.
\end{itemize}
}

\cventry{Mar 2020 -- Aug 2020}{IT Operations Manager}{\textbf{Company C}}{City, Country}{}{
\begin{itemize}
    \item Led a team of 15, managed vendor relationships, and supported over 1,000 users.
    \item Managed IT infrastructure for a new campus launch and ensured seamless integration.
    \item Implemented remote working tools and business continuity solutions during the COVID-19 crisis.
\end{itemize}
}

\cventry{Aug 2017 -- Mar 2020}{Change & Problem Manager}{\textbf{Company D}}{City, Country}{}{
\begin{itemize}
    \item Managed change processes and resolved IT issues across all sites in the region.
    \item Handled an IT budget of CHF 1.5 million for Backup and Object Storage projects.
    \item Revised change management process to achieve ISO 9001 certification and align with ITIL standards.
\end{itemize}
}

\cventry{Feb 2012 -- Jan 2014}{Team Leader}{\textbf{Company E}}{City, Country}{}{
\begin{itemize}
    \item Led a global team of 50 across 16 countries, managing 40,000 Windows servers.
    \item Implemented IT security best practices, server hardening, and disaster recovery plans.
    \item Responsible for technical training and performance management of the team.
\end{itemize}
}

\cventry{2010 -- 2012}{EMEA IT and Security Manager}{\textbf{Company F}}{City, Country}{}{
\begin{itemize}
    \item Developed IT strategy across multiple sites, overseeing infrastructures, software, and support services.
    \item Managed security protocols, audits, and GDPR compliance.
    \item Supervised a team of 15 IT professionals across the region.
\end{itemize}
}

\cventry{Jul 2008 -- Jan 2010}{IT Manager, Headquarters}{\textbf{Company G}}{City, Country}{}{
\begin{itemize}
    \item Managed IT operations for the headquarters, serving 600 users.
    \item Led an expansion project involving server room creation and PBX systems.
    \item Managed the IT budget, contracts, and key projects.
\end{itemize}
}
